Democracy, Public Support, and Measurement Uncertainty

### 2021-05-03 paper/dcpo_demsupport.Rmd
ifelse doesn't work for mi weirdly, trying if_else perhaps

tidy_result_clsUncertain <- map(ls_mod, possibly(function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_vars <- ifelse(class(result[[1]])[1] == "plm", 
                        mitools::MIextract(result, fun = vcovBK_se),
                        mitools::MIextract(result, fun = vcovHC_se))
  result_betas <- mitools::MIextract(result, fun = coef)

  summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))
}, otherwise = NA_real_))

>>>>

tidy_result_clsUncertain <- map(ls_mod, function(aMod){ # reading a model
  result <- map(df_cls, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  ## Not work with ifelse
  result_vars <- ifelse(class(result[[1]])[1] == "plm", 
                        eval(mitools::MIextract(result, fun = vcovBK_se)),
                        eval(mitools::MIextract(result, fun = vcovHC_se)))

  summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))
})
